---
title: "Activity report"
author: "oneScientist"
date: "20 décembre 2015"
output: html_document
---

### Loading and preprocessing the data

First, load the data from the "activity.csv" file.

```{r}
activity <- read.csv("activity.csv")
```

No nead for preprocessing the data.

### What is mean total number of steps taken per day?

1. The total number of steps taken per day

```{r}
total_number_steps_per_day <- aggregate( steps~date, activity, sum)

hist(total_number_steps_per_day$steps, main = "The total number of steps taken per day", xlab = "The total number of steps taken per day", ylab = "value")
```

2. The mean and median of the total number of steps taken per day

The mean of the total number of steps taken per day

```{r}
mean_steps <- mean(total_number_steps_per_day$steps)
mean_steps
```

The median of the total number of steps taken per day

```{r}
median_steps <- median(total_number_steps_per_day$steps)
median_steps
```

### What is the average daily activity pattern?

1. the number of steps taken per interval averaged across all days

First, we compute the number of steps average per interval across all days

```{r}
activityAverageInDay <- aggregate(steps ~ interval, activity, mean)
```

```{r}
plot.ts(activityAverageInDay$interval, activityAverageInDay$steps, main = "the number of steps taken per interval averaged across all days", xlab = "Interval", ylab = "Number of Steps Average")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
activityAverageInDay[which.max(activityAverageInDay$steps),]$interval
```

### Imputing missing values

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(complete.cases(activity) != TRUE)
```

