---
title: "Reproducible Research - Assignement 1"
author: "oneScientist"
date: "21 janvier 2016"
output: html_document
---

## Load needed libraries

```{r}
library(ggplot2)
library(knitr)
```

## Read data

```{r}
dat <- read.csv("activity.csv")
```


## Mean total number of steps taken per day

The total number of steps taken per day

```{r}
totalNbStepsPerDay <- tapply(dat$steps, dat$date, function(x) sum(x, na.rm = TRUE))
totalNbStepsPerDay

hist(totalNbStepsPerDay, main = "Total number of steps taken per day", xlab = "Number of steps", col = "green")
```

The mean of the total number of steps taken per day

```{r}
mean(totalNbStepsPerDay)
```


The median of the total number of steps taken per day

```{r}
median(totalNbStepsPerDay)
```

## Average daily activity pattern

```{r}
meanStepsPerInterval <- tapply(dat$steps, dat$interval, function(x) mean(x, na.rm = TRUE))

plot(cbind(as.numeric(names(meanStepsPerInterval)), meanStepsPerInterval), type = "l", main = "Mean of steps per interval taken all days", xlab = "Intervals", ylab = "Mean of steps per interval")
```

The interval containing the maximum number of steps 

```{r}
which.max(meanStepsPerInterval)
```

The interval is 835.


## Imputing missing values

Calculate and report the total number of missing values in the dataset

```{r}
sum(!complete.cases(dat))
```

For missing values, we compute the mean of the number of steps per interval.
For each missing number of steps, we replace the "NA" value by the mean for the same interval.

So, first, we compute the indices of the NAs steps values.

For each NA steps value, we replace with the average number of steps for the same interval. 

```{r}
dataWithoutNAs <- dat
naSteps <- which(is.na(dataWithoutNAs$steps))

for(i in naSteps){
    dataWithoutNAs[i,"steps"] <- meanStepsPerInterval[as.character(dat[i,"interval"])]
}
```


The total number of steps taken per day after imputing NA values

```{r}
totalNbStepsPerDayNoNA <- tapply(dataWithoutNAs$steps, dataWithoutNAs$date, function(x) sum(x, na.rm = TRUE))

hist(totalNbStepsPerDayNoNA, main = "Total number of steps taken per day after imputing NAs values", xlab = "Number of steps", col = "green")
```

The mean of the total number of steps taken per day after imputing NA values

```{r}
mean(totalNbStepsPerDayNoNA)
```


The median of the total number of steps taken per day after imputing NA values

```{r}
median(totalNbStepsPerDayNoNA)
```


## Comparing activity patterns between weekdays and weekends


```{r}
# Create the new variable for weekend day and week day
dataWithoutNAs$weekday <- weekdays(as.Date(dataWithoutNAs$date, "%Y-%m-%d"))
dataWithoutNAs <- transform(dataWithoutNAs, weekday = ifelse(weekday %in% c("samedi", "dimanche", "saturday", "sunday"), "weekend", "weekday"))
   
stepsByIntervalMean2 <- aggregate(steps ~ interval + weekday, data=dataWithoutNAs, mean)
colnames(stepsByIntervalMean2) <- c("Interval","weekend","avgSteps")


plot <- ggplot(stepsByIntervalMean2, aes(Interval, avgSteps)) + 
    geom_line(col = "blue") + 
    facet_grid(weekend ~ .) +
    xlab("Interval") + 
    ylab("Average Steps in Interval")

plot
```
